---
title: "Working Directories for Python in RStudio (Success)"
author: "Chris Prener"
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output: 
  github_document: default
  html_notebook: default 
---

```{r setup, include=FALSE}
reticulate::use_python("/usr/local/bin/python3")
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

## Introduction
This notebook illustrates one challenge of integrating Python into our lab's existing RStudio workflows - we typically place notebooks in a `docs/` folder within the main repo. All data is stored in a `data/` folder. 

This creates a challenge for managing the Python side of the notebook, because the working directory defaults to the same directory the notebook is stored in. In `R`, we would use the `here::here()` function to overcome this. Instead, we set the `root.dir` option for `knitr`.

## Dependencies
This notebook requires the `reticulate` package as well a number of other packages (`ggplot2` and `magrittr`) for illustration purposes.

```{r load-packages-r}
# tidyverse packages
library(ggplot2)          # plotting
library(magrittr)         # pipe operator

# other packages
library(reticulate)       # python integration
```

This notebook also requires a couple of Python libraries as well - `os` for interacting with the operating system and `pandas` for illustration purposes. 

```{python load-packages-py}
import os
import pandas as pd
```

## Check Working Directory
Quickly, we'll check the Python working directory:

```{python check-wd-py}
print(os.getcwd())
```

Note that this pointing to the project folder instead of the `docs/` folder. This is the expected behavior now that we have modified the `setup` chunk above.

## Load Data
This notebook requires data stored in `data/`, which we'll initial load into a data frame using `pandas` first:

```{python load-data-py}
cars = pd.read_csv("data/mpg.csv")
```

## Plot Data
We'll now plot the `cars` data from the `pandas` data frame:

```{r plot-from-py}
py$cars %>%
  ggplot(mapping = aes(hwy, cty)) +
  geom_point(position = "jitter")
```
